The \dealii{} Library, Version 8.5

### 2017-03-10 8.5/paper.tex
Amend discussion on linear operator extensions

The \texttt{LinearOperator} class has been extended by a generic
``payload'' mechanism that allows to attach arbitrary additional
information to a \texttt{LinearOperator}. This was achieved by introducing
a generic \texttt{Payload} base class. The main use case of the new
mechanism is to extend the \texttt{LinearOperator} class to seamlessly
exploit the native features and operations offered by external linear
algebra libraries. We have thus developed a \texttt{TrilinosPayload} class,
that provides full support for the suite of {\trilinos} parallel iterative
solvers and preconditioners.

A particular interesting case is the construction of an
\texttt{inverse\_operator}. Now both, \dealii's built in solvers and those
offered by {\trilinos}, can be selected. This has been achieved by using
the \texttt{Epetra\_Operator} as the basis for the
\texttt{TrilinosPayload}, for which the result of standard and composite
operations involving forward (\texttt{Apply()}) and inverse
(\texttt{ApplyInverse()}) matrix-vector multiplication are collated using
lambda functions.

>>>>

The \texttt{LinearOperator} class has been extended by a generic
``payload'' mechanism that allows for the attachment of arbitrary additional
information to a \texttt{LinearOperator}. This was achieved by introducing
a generic \texttt{Payload} base class. The main use case of the new
mechanism is to extend the \texttt{LinearOperator} class to seamlessly
exploit the native features and operations offered by external linear
algebra libraries. We have thus developed a \texttt{TrilinosPayload} class
that provides full support for the suite of {\trilinos} parallel iterative
solvers and preconditioners.

A particularly interesting case is the construction of an
\texttt{inverse\_operator}. Whereas previously only \dealii's built-in solvers
were compatible with this operator, now both them and those
offered by {\trilinos} can be selected. This has been achieved by using
the \texttt{Epetra\_Operator} as the basis for the
\texttt{TrilinosPayload}, for which the result of standard and composite
operations involving forward (\texttt{Apply()}) and inverse
(\texttt{ApplyInverse()}) matrix-vector multiplication are collated using
lambda functions.
